When are Fuzzy Extractors Possible?

### 2014-09-23 info-bounds/FuzzyExtPossibility.tex
working on isoparametric inequality proof

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce adversary, then there is no hope for security~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(m^*, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.  However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.

Before turning to our results we separate between two types of fuzzy extractors and secure sketches.  The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.  We call this type of algorithm distribution-oblivious.  We define a new type of algorithm that called distribution-aware that is allowed to know the precise distribution to be supported.  We provide a definition for secure sketches~(this definition can easily be extended to fuzzy extractors)

\begin{definition}
Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  Note correctness is guaranteed only for the support of $W$.
\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.  When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.  It is not clear how to meaningfully define efficient distribution aware algorithms.  If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.  This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.

We begin with by showing that secure sketches and fuzzy extractors are possible in the distribution aware setting whenever there is super-logarithmic fuzzy min-entropy.  We then turn to the standard \emph{distribution oblivious} setting.

@@

\begin{table}
\begin{tabular}{l | l | c}
Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
\hline
Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$ & $\log |B_t|$
\end{tabular}
\caption{Residual entropy of secure sketches for complete recovery.}
\label{tab:upper bounds}
\end{table}
\bnote{Fix right side of table}
\bnote{the table should move.}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

\section{Distribution-Aware  Sketches}
In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

\subsection{Well-Spread Distributions}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
We begin by defining a well-spread distribution.

\begin{definition}
A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
\end{definition}
Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result can be viewed as saying that well-spread distributions are not interesting in the distribution-aware setting.  However, we will show that providing secure sketches for well-spread distributions in the distribution-oblivious setting is impossible.}

\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, m,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
\end{lemma}  
\begin{proof}
It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
\[
t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
\end{proof}

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\bnd}{\ensuremath{\class{Bnd}}\xspace}
\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(m^*, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.  However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.  Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.

We separate between two types of fuzzy extractors and secure sketches.  The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.  This is because we rarely have complete distributions of a physical probability distribution. We call this type of algorithm distribution-oblivious.  We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} 
\[
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta\]
 where the probability is taken over the coins of $\sketch$ and $\rec$.  Note correctness is guaranteed only for the support of $W$.
\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.  One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.  Our constructions do not work in this setting.\bnote{why am I talking about this?}

@@

\begin{table}
\begin{tabular}{l | l}
Lower bounds & Residual Entropy\\
\hline
Well-spread distribution & $\Hfuzz(W)$ \\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
\end{tabular}
\caption{Summary of results for distribution aware setting.  Residual entropy of distribution-aware secure sketches with error $\delta$.}
\label{tab:upper bounds}
\end{table}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

\subsection{Well-Spread Distributions}
\bnote{is this section useful?}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
We begin by defining a well-spread distribution.

\begin{definition}
A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
\end{definition}
Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
\end{lemma}  
\begin{proof}
It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
\[
t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
\end{proof}

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.  %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.  
An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.  That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
\end{align*}
Setting $\ell = m$ yields
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

\begin{corollary}
\label{cor:extension to fuzz ext}
Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.  (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
\end{corollary}

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Distribution-Oblivious Sketches}
\label{sec:dist oblivious}
